### 2017-04-18 paper/evaluation.tex
Adjusted format

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
Kite SDK & - & - & - & - & - & -\\%
Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
OpenMRS Core & - & - & - & - & - & -\\%
Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
Apache Eagle & - & - & - & - & - & -\\%
Geotools & - & - & - & - & - & -\\%
Atomix & - & - & - & - & - & -\\%
Kuromoji & - & - & - & - & - & -\\%
\Fix{Snazy OHC} & - & - & - & - & - & -\\%
\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
\emph{Subject} & \Seq{} & \SeqClassParMeth{} & \ParClassSeqMeth{} & \ParClassParMeth{} & \ForkSeq{} & \ForkParMeth{}\\%
\midrule%
%% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
%% Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
Kite SDK & - & - & - & - & - & -\\%
%% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
OpenMRS Core & - & - & - & - & - & -\\%
%% Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
Apache Eagle & - & - & - & - & - & -\\%
Geotools & - & - & - & - & - & -\\%
Atomix & - & - & - & - & - & -\\%
Kuromoji & - & - & - & - & - & -\\%
\Fix{Snazy OHC} & - & - & - & - & - & -\\%
\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Tabela de eficiencia}}
\label{tab:rq6-efficiency}
\end{figure}
